---
title: ""
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Motivation

The goal of this function is to produce a standardized output for predictions using parsnip binary classification models.

The output of this function will include:

1. The 'truth' (that is, what the actual outcome was)
2. The predicted probability for each class (restricted to only two classes)
3. The predicted response class based on the predicted probability of the "positive class"
```{r load libraries, message=FALSE}
library(tidyverse)
library(glue)
library(tidymodels)
```

We will use the LendingClub data available in the parsnip package to demonstrate how this function works.
```{r load data}
class_data_tbl <- parsnip::lending_club %>%
  select(Class, funded_amnt:sub_grade, annual_inc, emp_length, revol_util)

class_data_tbl


split_obj <- initial_split(class_data_tbl, prop = 0.8, strata = "Class")
train_tbl <- training(split_obj)
test_tbl  <- testing(split_obj)


model_logit_obj <- logistic_reg(mode = "classification") %>%
  set_engine("glm") %>%
  fit(Class ~ ., data = train_tbl)

tidy(model_logit_obj)
```


## Manual Method

We can manually compute each component of this function's planned output as follows:

1. The Truth
```{r}
truth_tbl <- test_tbl %>% 
  select(Class) %>% 
  set_names("truth")

truth_tbl
```

2. The Predicted Probabilities
```{r}
probs_tbl <- model_logit_obj %>% 
  predict(new_data = test_tbl, type = "prob") %>% 
  set_names(str_remove_all(names(.), ".pred_"))

probs_tbl
```

3. The Predicted Outcome Classes
```{r}
threshold <- 0.5
levels    <- test_tbl %>% pull(Class) %>% levels()

preds_tbl <- probs_tbl %>% 
  mutate(
    prediction = case_when(
      good >= threshold ~ "good",
      TRUE              ~ "bad"
    ) %>% factor(levels = levels)
  ) %>% 
  select(prediction)

preds_tbl
```

Can combine the previous together into the goal output tibble
```{r}
output_tbl <- truth_tbl %>% 
  bind_cols(probs_tbl) %>% 
  bind_cols(preds_tbl)

output_tbl
```


## predict_binary() Function

The predict_binary() function automates the aforementioned process
```{r load function, echo = FALSE}
source("../../functions/predict_binary.R")
```

```{r function demo}
model_predictions_tbl <- model_logit_obj %>% 
  predict_binary(new_data = test_tbl, response = Class, positive = "good")

model_predictions_tbl
```

The function provides various arguments, such as .thresh that allows the user to change the probability threshold that determines which the outcome class is, and .verbose that keeps the user informed as to where the function is executing

```{r arguments}
model_predictions_tbl <- model_logit_obj %>% 
  predict_binary(new_data = test_tbl, response = Class, positive = "good", .thresh = 0.95, .verbose = TRUE)

model_predictions_tbl
```
